%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

%In case you encounter the following error:
%Error 1010 The PDF file may be corrupt (unable to open PDF file) OR
%Error 1000 An error occurred while parsing a contents stream. Unable to analyze the PDF file.
%This is a known problem with pdfLaTeX conversion filter. The file cannot be opened with acrobat reader
%Please use one of the alternatives below to circumvent this error by uncommenting one or the other
%\pdfobjcompresslevel=0
%\pdfminorversion=4

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{subcaption}
%\usepackage{graphicx}
\usepackage{wasysym}
\usepackage{ulem} 
\usepackage{tcolorbox}
\usepackage{booktabs} % for bottomrule, toprule, cmidrule
\usepackage{siunitx}
\usepackage{textcomp}

% my own style file
\input{paper_style.sty}


\title{\LARGE \bf
From Milliseconds to Microseconds: Optimizing the Static Forward Kinematics of CTCRs for use in Real-Time Systems
% On Runtime Reduction in... by...
}


\author{Taqi Hamoda, Reinhard M.~Grassmann, and Jessica Burgner-Kahrs, \textit{Senior Member, IEEE}% <-this % stops a space
\thanks{We acknowledge the support of the Natural Sciences and Engineering Research Council of Canada (NSERC), [RGPIN-2019-04846].}
\thanks{All authors are with Continuum Robotics Laboratory, Department of Mathematical and Computational Sciences, University of Toronto, Mississauga, ON L5L 1C6, Canada {\tt\small reinhard.grassmann@utoronto.ca}}%$^{1}$
}


\begin{document}


\maketitle
\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

\commentblock{
Efficient computation of the forward kinematics (FK) for concentric tube continuum robots (CTCRs) is essential for real-time control and deployment.
However, the current gold-standard model, the static Cosserat rod model, is computationally intensive, limiting its use in high-frequency applications.
Despite various optimization efforts, a universal strategy that achieves real-time performance has remained elusive.
We tackle this challenge by applying a series of numerical optimizations, including explicit integration techniques, quaternion-based orientation representation, and efficient Jacobian updating schemes.
These optimizations reduce function calls by up to 90\% without sacrificing accuracy, achieving a runtime of just 120 microseconds for FK computation, enabling real-time control while ensuring universal applicability across various architectures and systems.
Additionally, we introduce a novel, computationally accessible proxy for elastic stability, which could enable the detection of snapping behavior in CTCRs.
}

\bulletpoints{
    \item Topic Sentence: Give a brief overview of the problem/challenge the paper is trying to address, how the paper addresses this challenge/what our contribution to the field is, and the results we obtained.
    \item The challenge that we are trying to solve is that the Cosserat Rod model is not as efficient as it could be. There is still potential for a more universal optimization strategy.
    \item Proof that this indeed is a problem is that there are many papers that attempt to optimize the kinematics model, with varying degrees of success.
    \item Our method is to apply different numerical optimizations to the solver and integrator instead of modifying the actual problem core (instead of tweaking a car's engine to make it faster, we optimize the chassis to make it as aerodynamic as possible).
    \item Discuss why our method differs from the current state of the art.
    \item Our method provides universal optimization to the model regardless of the architecture or the actuation system. For a regular CTCR, we bring the runtime down to 120 us.
    \item I also want to briefly mention that we might have found a reliable numerical proxy/indicator for elastic stability.
}

\end{abstract}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%===============================================================================
% Introduction
\input{Introduction/introduction}

%===============================================================================
% The Forward Kinematics
\input{The Boundary Value Problem/bvp}

%===============================================================================
% Methods
\input{Methods/methods}

%===============================================================================
% Evaluation
\input{Evaluation/evaluation}

%===============================================================================
% Discussion
\input{Discussion/discussion}

%===============================================================================
% Conclusion
\input{Conclusion/conclusion}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
%                                   % on the last page of the document manually. It shortens
%                                   % the textheight of the last page by a suitable amount.
%                                   % This command does not take effect until the next page
%                                   % so it should come on the page before the last. Make
%                                   % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{ACKNOWLEDGMENT}
The authors would like to thank Sébastien Briot and Andrea Gotelli for discussions aiding in the conceptualisation of this paper.


\addcontentsline{toc}{section}{REFERENCES}
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv, literature}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}